Circumpolar variations in Southern Ocean eddy dynamics:\\An ensemble approach

### 2021-06-14 paper/main.tex
writing some text

\newcommand{\navidcomment}[1]{{\color{red} [#1]}}
\newcommand{\andycomment}[1]{{\color{Green} [#1]}}

@@

\subsection{Calculating geouv from SSH, removing trends, etc. (Sally)}

\subsection{TKE and filtering  to eliminate seasonal signal}

>>>>

\newcommand{\navidcomment}[1]{{\color{red} [#1]}}
\newcommand{\andycomment}[1]{{\color{blue} [#1]}}

@@

\andycomment{Thierry could add more if needed?}

\subsection{Estimating geostrophic eddy velocity}
For each ensemble member, the sea surface height, $\eta_i$, is saved as a 5-daily average (where $i$ represents the ensemble member) . 
The sea level anomaly, $\eta_i'$ is calculated as the transient component of sea level, given by 
\[ \eta_i' = \eta_i - \overline{\eta_i}\]
where $\overline{\cdot}$ represents the temporal average over the simulation.
The sea level anomaly is detrended, and then used to calculate the eddy velocity field.
Surface eddy velocity in each ensemble member, $\mathbf{u}_i' = (u_i', v_i')$ is estimated from the detrended sea level anomaly via the geostrophic relation,
\[u_i' = - \frac{g}{f} \frac{\partial \eta_i'}{\partial y}; \quad v_i' = \frac{g}{f} \frac{\partial \eta_i'}{\partial x}\]
where $g$ is the acceleration due to gravity and $f$ is the local Coriolis parameter.
Anomalous values of $\mathbf{u}_i'$ close to coastlines are removed.

\andycomment{Sally to add details about SLA processing?}

\subsection{Calculating eddy kinetic energy}
The surface eddy kinetic energy for each ensemble member is calculated as 
\[E_i = \frac{1}{2}(u_i'^2 + v_i'^2)\]
and subsampled at monthly temporal resolution.
